### 2015-01-22 publishing/plos_template.tex
dte's edits made

Although additive manufacturing methods have been under development and use for more than 30 years, 3D printing has experienced a sudden surge in popularity due to recent availability of consumer desktop printers. 
Inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software movement and has spawned the additional areas of open source hardware, such as circuit boards computers (Arduino, Raspberry Pi) as well as 3D printers themselves (RepRap).
Open source scientific instruments and laboratory equipment as also being actively developed.
A 3D-printable piece of lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the material. 
This may allow a researcher, an opportunity to preform a measurement, or activity with out typical financial and time constraints and with the option of further customizing the printed object.
Some of the more clever printable parts that have emerged  are ones that give a new function to a existing device where before there was none.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges.

Printable micropipette designs can be found on 3D-part sharing websites.
While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.

>>>>

3D printing as a form of additive manufacturing has existed for decades althought the recent avalibilty of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software movement and has spawned the additional areas of open source hardware, such as microcontroller boards (Arduino) as well as 3D printers themselves (RepRap).
Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.)
3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material. 
In addition, end users can customize the equiment to their application. 
Some of the more clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some finacial barriers of entry.

Printable micropipette designs can be found on 3D-part sharing websites (thiniverse).
While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes nor have any been rigorously validated.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
